\documentclass[oneside,danish,onecolumn,openbib,a4paper]{memoir}
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage{siunitx,mathtools}
\usepackage{hyperref}
\hypersetup{colorlinks=true}
\title{You're a side character in a story. By chance you become aware of this fact and you try everything to be more relevant to the story, even going as far as to intefere in the protagonist's life.}
\author{Thorbjørn Erik Køppen Christensen}
\begin{document}
\maketitle{}

Catherine and I had won the science fair yesterday, and earlier today she told me that NASA had contacted her, asking her to join the team designing the Mars base. 
Now it's not like she's not nice, but it was our shared project, so I couldn't help to ask: ``Why not me?''
and the only real answer I could come up with was that I was more of a side character in her story, a speck of dust in her larger master piece. 
This could not be true, it was unacceptable to me, so I did the only reasonable thing, and started taking the spotlight from her.
When we won the year later, I made sure MY name was on top, that my contributions were larger!\newline
When we went to university, I made sure MY hand ins were always better.\newline
When we started looking for love, I made sure I got the best guy first.\newline
When we send in our Ph.D.'s, I made sure MINE would be rated the best.\newline
When we started looking for jobs, I made sure I got the best one.\newline
When we started looking for families, I made sure MINE was nicer!

When she crashed, i made sure I was there for HER in the hospital.\newline
When she felt sad, that NASA had suddenly retracted HER invitation I cried with her.\newline
When she discovered she could carry no child, I gave her all the support I could.\newline
When she needed a kidney, who's could she get but mine?\newline
When we were up for a promotion, what could I do but recommend that her genius got the position?\newline
\newline\newline\newline
Feedback welcome ;-)

\subsection{Inspired by:}
\url{https://www.reddit.com/r/WritingPrompts/comments/ad58u0/wp_youre_a_side_character_in_a_story_by_chance/}
\end{document}
