\documentclass[oneside,danish,onecolumn,openbib,a4paper]{memoir}
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage{siunitx,mathtools}
\usepackage{hyperref}
\hypersetup{colorlinks=true}
\title{You've been recruited into an adventuring party full of rejects. The warrior faints at the sight of blood, the wizard's spells never do what he intends, and the cleric is an atheist. As a tone-deaf bard, you're sure that you'll fit right in.}
\author{Thorbjørn Erik Køppen Christensen}
\begin{document}
\maketitle{}

``None of you'll walk out of here alive!'' Nefus, the black and messy god of death, screamed wildly in a shrill but a fainting voice, drawing it's last breath.
If there's one thing all the gods are really bad ad, it's having a guy/gal standing next to them who strongly opposes the idea that a god should exist.
That's why we always got the god jobs: 
We had Eyra the green.
Why she had gained the name ``the green'' had always stood out to me as weird, why not ``the disbeliever'', ``the heretic'',  or ``the godslayer''?
She wasn't new in the business of slaying the gods either, so ``the green'' really never made sense to me.
Maybe it was because she thought she didn't believe, yet she was a stronger believer than any other, her belief just being that no god could exist?\newline\newline
\begin{centering}
       ``Thou who wishes \newline
       Lives on dishes\newline
       Shall no more\newline
       exist as lore! \newline\newline
       Today I say\newline
       be on thee way\newline
       you'll be forgot\newline
       you ain't no god!{``}\newline

\end{centering}

As I spoke the poem the last of Nefus's godly power left the body and left behind a young man, Kasidus.
Kasidus spoke: ``Al I really wish to do is kill these god damn things, why will it never work?, why do I always end up getting possessed by the freaks???''
And while there is some truth to his tale, he doesn't quite fathom how important he is for the killing of the gods. 
I will however say that I can understand the man, I wouldn't like the idea of being possessed by a god every time I wanted to boil some water with my magic!

As Yhil smacked the remaining cult followers down, the other three of us started unpacking our rope, to tie up the ones already down.
While she cannot see blood and still stand, she's really good at fighting, and the bounties are often higher for living criminals, so that's just a win win for us!


Feedback welcome ;-)
\subsection{Inspired by:}
\url{https://www.reddit.com/r/WritingPrompts/comments/acpgpi/wp_youve_been_recruited_into_an_adventuring_party/}
\end{document}
