\documentclass[oneside,english,onecolumn,openbib,a4paper]{memoir}
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage{siunitx,mathtools}
\usepackage{hyperref}
\hypersetup{colorlinks=true}
\title{Once a day, your magic 8 ball has the power to make any request come true. The catch: the chance of having your wish granted depends on the size of the request you make.}
\author{Thorbjørn Erik Køppen Christensen}
\begin{document}
\maketitle{}

Some people spent every day of their lives hoping for the big win: ``Make 10 billion \$ fall on the earth in front of me.'', some of those were lucky, but most never got what they wanted. 
In my eyes it was honestly a bad way of using the daily wish, since smaller wishes had a larger chance of coming through. 
I would often spend my wishes on smaller stuff: ``give me a nice meal for dinner'' would only rarely go unheard, but wasn't the smartest of wishes either.
If one wanted to be clever with their wishes it was smart to wish forgetfulness or the like on others, no big mistakes for sure, but the small stuff always worked out!
See that guy standing over there, he seemed like one of the lucky few, probably has a million or two in his pouch, and it wouldn't mean anything if he lost it, or forgot it. 
This would not help one, if one was not ready to take was what forgotten, but it was a quick way of making millions fairly surely, all one really had to do was get to the rich part of town.
After one had gained some wealth, the easiest thing to do was to put some money in stock, then wish for small things happening nicely for the stock; ``Let that big ship get well through the panama canal.'' or ``Please let no pirates attack.''
At that point, one would pretty much be settled, for life.
\newline\newline\newline
Feedback welcome ;-)

\subsection{Inspired by:}
\url{https://www.reddit.com/r/WritingPrompts/comments/adeju8/wp_once_a_day_your_magic_8_ball_has_the_power_to/}
\end{document}
